The occurrence rate of long-period exoplanets

### 2016-02-07 document/ms.tex

\documentclass[12pt,preprint]{aastex}

@@

\usepackage{natbib}
\bibliographystyle{apj}

@@

\newcommand{\figref}[1]{\ref{fig:#1}}
\newcommand{\Fig}[1]{\figurename~\figref{#1}}
\newcommand{\fig}[1]{\Fig{#1}}
\newcommand{\figlabel}[1]{\label{fig:#1}}

\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\tab}[1]{\Tab{#1}}
\newcommand{\tablabel}[1]{\label{tab:#1}}

\renewcommand{\eqref}[1]{\ref{eq:#1}}
\newcommand{\Eq}[1]{Equation~(\eqref{#1})}
\newcommand{\eq}[1]{\Eq{#1}}
\newcommand{\eqalt}[1]{Equation~\eqref{#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}

@@

@@

\title{%
Automated detection \& characterization of long-period transits in the
\kepler\ archive
}

\newcommand{\uw}{3}
\newcommand{\nyu}{4}
\newcommand{\cds}{5}
\newcommand{\mpia}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,2,\uw},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Eric~Agol\altaffilmark{\uw},
    and others
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@uw.edu}}
\altaffiltext{2}         {Sagan Fellow}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\cds}      {Center for Data Science, New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
We are grateful to the entire \kepler\ team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission
and the successes of \KT, present and future.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}

>>>>

\documentclass[onecolumn]{aastex6}

@@

\usepackage{natbib}
\bibliographystyle{aasjournal}

@@

% \newcommand{\figref}[1]{\ref{fig:#1}}
% \newcommand{\Fig}[1]{\figurename~\figref{#1}}
% \newcommand{\fig}[1]{\Fig{#1}}
\newcommand{\figlabel}[1]{\label{fig:#1}}

% \newcommand{\Tab}[1]{Table~\ref{tab:#1}}
% \newcommand{\tab}[1]{\Tab{#1}}
\newcommand{\tablabel}[1]{\label{tab:#1}}

% \renewcommand{\eqref}[1]{\ref{eq:#1}}
% \newcommand{\Eq}[1]{Equation~(\eqref{#1})}
% \newcommand{\eq}[1]{\Eq{#1}}
% \newcommand{\eqalt}[1]{Equation~\eqref{#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}

@@

% \slugcomment{Not to appear in Nonlearned J., 45.}

@@

\title{%
The occurrence rate of long-period exoplanets
}

\newcommand{\uw}  {Astronomy Department, University of Washington,
                   Seattle, WA, 98195, USA}
\newcommand{\nyu} {Center for Cosmology and Particle Physics,
                   New York University,
                   4 Washington Place, New York, NY, 10003, USA}
\newcommand{\cds} {Center for Data Science, New York University,
                   726 Broadway, 7th Floor, New York, NY, 10003, USA}
\newcommand{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                   K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\newcommand{\mpis}{Max Planck Institute for Intelligent Systems
                   Spemannstrasse 38, 72076 T\"ubingen, Germany}

\author{Daniel~Foreman-Mackey\altaffilmark{1,2}}
\affil{\uw}

\author{David~W.~Hogg}
\affil{\nyu \\ \mpia \\ \cds}

\author{Bernhard~Sch\"olkopf}
\affil{\mpis}

\author{Eric~Agol}
\affil{\uw}

\and

\author{and others}

\altaffiltext{1}{\url{danfm@uw.edu}}
\altaffiltext{2}{Sagan Fellow}

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
We are grateful to the entire \kepler\ team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission
and the successes of \KT, present and future.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.
Computing resources were provided by High Performance Computing (HPC) at New
York University (NYU).

\facility{Kepler}
